%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\def\verbose{0}

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Soo Kim -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> 16, Seorim 11ga-gil, Gwanak-gu,\\ % Address line 1
\> Seoul, 08840, Republic of Korea \\ % Address line 2
{\bf Date of Birth} \> 25$^{th}$ September 1991 \\ % Date of birth 
{\bf Nationality} \> Republic of Korea % Nationality
\end{tabbing}
}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +82 10 8560 6797 \\ % Mobile phone
{\bf Email} \> \href{mailto:carlsagan96@gmail.com}{carlsagan96@gmail.com} \\ % Email address
{\bf linkedin} \> \href{https://www.linkedin.com/in/soo-kim-carlsagan96/}{soo-kim-carlsagan96} \\
{\bf Github} \> \href{https://github.com/carlsagan21}{carlsagan21}
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

Research Assistant at Programming Research Laboratory ROPAS, Computer Science and Engineering, Seoul National University.\\
Interested in program analysis, distributed computing, clustering, and the-state-of-art techniques in web development from front-end to architecture.

%----------------------------------------------------------------------------------------
%	Research Experience SECTION
%----------------------------------------------------------------------------------------

\section{Research Experience}

\job
{Jul 2017 -}{Present}
{Programming Research Laboratory, Seoul National University}
{http://ropas.snu.ac.kr/}
{Research Assistant}
{Automated program corrector using machine learning.\\
%Automated program error localization using SAT-solver.\\
\rule{0mm}{5mm}{Technologies:} Tensorflow, seq2seq}

%------------------------------------------------

\if\verbose1
\job
{Mar 2015 -}{Aug 2016}
{Jang’s Lab for Human Nature Studies and Philosophy of Biology, Seoul National University}
{}
{Research Assistant}
{Researched Cultural Evolution, Morality and Sociality at Transdisciplinary Research Center for Culture-Brain Dynamics}
\fi

%----------------------------------------------------------------------------------------
%	Work Experience SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\job
{Dec 2015 -}{Aug 2016}
{Ab180, Seoul, Republic of Korea}
{https://airbridge.io/}
{Front-end Developer}
{Airbridge (Mobile app marketing performance analytics) https://airbridge.io/

Developed front-end web alone using React.

Attracted the 600M won(540,000\$) investment from TIPS. http://www.jointips.or.kr/\\
\rule{0mm}{5mm}{Technologies:} React, Redux, Webpack, D3, Eslint, Flow, Enzyme, Amazon S3, Jenkins, Flask, Amazon E2. / As a team, Scrum, JIRA, Confluence, Trello}

%------------------------------------------------

\if\verbose1
\job
{Sep 2011 -}{Jun 2013}
{Republic of Korea Army}
{}
{Sergeant}
{}
\fi

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\job
{Mar 2011 -}{Present}
{Seoul National University, Seoul, Republic of Korea}
{http://www.snu.ac.kr/index.html}
{College of Liberal Studies}
{
\textit{Candidate for Bachelor?s Degree in Computer Science Engineering}\\
\textit{Candidate for Bachelor?s Degree in Cognitive Studies of Religion}\\
4 Years Full Scholarship - \href{http://eng.kosaf.go.kr/jsp/main.jsp}{Korea Student Aid Foundation}\\
GPA: 3.75/4.3 \hspace{10mm} GPA(Major): 3.85/4.3\\
\rule{0mm}{5mm}{Related Courses:} Data Structures, Algorithms, Operating Systems, Creative Integrated Design, Programming Languages, Principles of Programming, Computer Architecture, Computer Programming, Hardware System Design, Logic Design, Electrical and Electronic Circuits, Discrete Mathematics
}

%------------------------------------------------

\job
{Sep 2016 -}{Feb 2017}
{Kyoto University, Kyoto, Japan}
{http://www.kyoto-u.ac.jp}
{Exchange Semester}
{
Overseas Study Abroad Support System Scholarship - \textit{480,000 yen(4800\$)} \href{http://www.jasso.go.jp/ryugaku/tantosha/study_a/short_term_h/index.html}{JASSO}\\
\rule{0mm}{5mm}{Related Courses:} Programming Languages
}

%\tabbedblock{
%\bf{Fall 2016} \> Exchange Semester - \href{http://www.kyoto-u.ac.jp}{Kyoto University}\\[5pt]
%\> GPA - 89.7/100\\
%\>\+
%\textit{Introduction to Classical Japanese Literature} - A \\
%\textit{Japanese Politics-E2} - A \\
%\textit{Contemporary Philosophy in Japan} - A \\
%\textit{Japanese Intellectual History II-E2} - A\\
%\textit{Philosophy of Religion B (Lectures)} in Japanese - A\\
%\textit{Programming Languages} in Japanese - B\\
%\textit{Philosophy of Religion (Seminars)} in Japanese - A+\\
%}

%------------------------------------------------

\job
{Jul 2014}{}
{Freie Universität Berlin, Berlin, Germany}
{http://www.fu-berlin.de/}
{Summer Semester}
{
}

%\tabbedblock{
%\bf{July 2014} \> Summer Semester - \href{http://www.fu-berlin.de/}{Freie Universität Berlin}\\[5pt]
%\>\+
%\textit{Islam and The West} \> A
%}

%----------------------------------------------------------------------------------------
%	Scholarships and awards SECTION
%----------------------------------------------------------------------------------------

\if\verbose1
\section{Scholarships and Awards}

\skillgroup{Overseas study abroad support system scholarship}
{
Oct 2016 - \href{http://www.jasso.go.jp/ryugaku/tantosha/study_a/short_term_h/index.html}{JASSO}\\
\textit{480,000 yen(4800\$)} - 80,000 yen / month\\
}

\skillgroup{SDE Excellent research}
{
Feb 2016 - \href{http://liberaleduenglish.snu.ac.kr/}{Dep. of Basic Education Center, Seoul National University}\\
\textit{Criticism of the Clash of Civilizations seen through Morocco Mawazine Festival: Focused on 'Family'} - 3,000,000 won(3000\$)\\
}

\skillgroup{A Chinese Classics Scholarship Student}
{
Mar 2013 - \href{http://www.kfas.or.kr/?pCulture=en}{Korea Foundation for Advanced Studies}\\
\textit{12,960,000 won(12,960\$)} - 360,000 won / month\\
It is a scholarship system for early selection of undergraduates who want to study oriental studies among the majors of humanities and social sciences, and to teach them the basic scriptures and major histories of the Chinese Classics Studies for three years and to help them grow into excellent scholars in the field of Oriental Studies.
}

\skillgroup{Humanities 100 years scholarship}
{
Mar 2011 - \href{http://eng.kosaf.go.kr/jsp/main.jsp}{Korea Student Aid Foundation}\\
\textit{4 years full scholarship}\\
}
\fi

%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\skillgroup{Hardware Accelerator (Hardware System Design)}
{
Processing System, Matrix-Vector Multiplication IP, BRAM for DNN. On FPGA in Verliog, Cpp, Python.\\
Caculation: 423.15\% faster than CPU (Benchmark using MNIST)
}
\skillgroup{Scheduler using Weighted Round Robin (Operating Systems)}
{
Task Scheduler running reasonable performance. In Kernel 3.10.
}
\skillgroup{Geo-tagged File System (Operating Systems)}
{
File system accessible according to the GPS of a mobile device. In Kernel 3.10.
}
\skillgroup{Rotation based Lock for Synchronization (Operating Systems)}
{
RWLock-like Lock according to the rotation of a mobile device. In Kernel 3.10.
}
\skillgroup{Async Web Engine (Creative Integrated Design)}
{
Project with \href{https://kr.tmaxsoft.com/main.do}{TmaxSoft}. Outperformed Nodejs marginally. In Java.
}
\skillgroup{Lisp Interpreter (Principles of Programming)}
{
Racket interpreter. In OCaml
}

%----------------------------------------------------------------------------------------
%	Languages SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\skillgroup{Korean}
{
Native
}

\skillgroup{English}
{
Business Level\\
TOEFL: 104/120 \hspace{10mm} GRE: Verbal 156/170, Quant. 170/170
}

\skillgroup{Japanese}
{
Business Level\\
Exchange semester in Japan
}

%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------
%
%\section{Software Engineering Skills}
%
%\skillgroup{Programming Languages}
%{
%\textit{Ruby} - MRI 1.8.7, 1.9.2\\
%\textit{ASP.NET, C\#, VB.NET}\\
%\textit{PHP}\\
%\textit{Java/Scala}
%}
%
%%------------------------------------------------
%
%\skillgroup{Web Development}
%{
%\textit{HTML5, CSS3/SASS, JavaScript/CoffeeScript/jQuery}\\
%\textit{Ruby on Rails v3.1}\\
%\textit{Test:Unit, RSpec, Cucumber, Selenium} - automated testing frameworks\\
%\textit{Apache/Nginx Web Servers}\\
%}
%
%%------------------------------------------------
%
%\skillgroup{Miscellaneous}
%{
%\textit{Microsoft SQL Server 2000/2005} - database architecture and administration\\
%\textit{Transact-SQL} - data definition and manipulation\\
%\textit{SQL Profiler} - performance tuning and debugging\\
%\textit{MySQL Server}\\
%\textit{CVS, DARCS, git} - source version control
%}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
%
%\section{Interests}
%
%\interestsgroup{
%\interest{Badminton, Tennis, Running, Cycling, Sailing}
%\interest{Travelling}
%\interest{Creative Writing}
%\interest{Photography}
%\interest{Car Mechanics}
%}

%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------
%
%\section{Referees}
%
%\parbox{0.5\textwidth}{ % First block
%\begin{tabbing}
%\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
%{\bf Name} \> Bill Lumbergh \\ % Referee name
%{\bf Company} \> Initech Inc. \\ % Referee company
%{\bf Position} \> Vice President \\ % Referee job title 
%{\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
%\end{tabbing}}
%\hfill % Horizontal space between the two blocks
%\parbox{0.5\textwidth}{ % Second block
%\begin{tabbing}
%\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
%{\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
%{\bf Company} \> Burbank Buy More \\ % Referee company
%{\bf Position} \> Store Manager \\ % Referee job title 
%{\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
%\end{tabbing}}

%----------------------------------------------------------------------------------------


\end{document}